Learning constraints in tabular data

### 2016-05-13 Paper/ECAI/tabular.tex
Comment
Corrections group generation

To reason over the groups, we automatically add to the constraint program a set of background facts that contain the properties of each group, namely its type, size and length. We also add all previously found constraints of constraint templates that are implied by this template. The actual constraints then express the properties defined in the signature, such as whether arguments are of a certain type, have certain dependencies or have to be equal length or orientation, etc.
\tias{More detailed description of the properties commented out, feel free to put in}
%Translation:
%\begin{description}
%  \item[Type] Require group that has supertype (e.g. integer => require numeric group, because subgroup might be integer)
%  \item[Length] Require group to have exact length (subgroups have the same length)
%  \item[Vectors / columns / rows] Require group to have at least the amount of vectors, columns, rows required
%  \item[Dependency] Fix dependent variables, for every assignment construct CSP that attempts to find values for the other variables
%  \item[Same length / table / orientation] Require groups to gave the same length table ...
%\end{description}

% TODO: old text, rephrase a bit
Constraints derived from the signature can usually but not always be enforced exactly on a group, as we have to consider whether subgroups could satisfy them.
For example, the \CSignature of ?? requires $v_r$ to be integer.
If a numeric group is assigned to $v_r$ then some subgroups may have type float while other may be of type integer, therefore, this group cannot be discarded.

@@

Note that for some constraint definitions, there are \textit{symmetries} over the arguments that lead to trivially equivalent solutions, for example $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. \tias{How are they stopped in the code? should be part of the pseud-code because not part of $Test(X)$?}

>>>>

To reason over the groups, we automatically add to the constraint program a set of background facts that contain the properties of each group, namely its type, size, number of columns and rows, length, orientation, and table. We also add all previously found constraints of constraint templates that are implied by this template. The actual constraints then express the properties defined in the signature, such as whether arguments are of a certain type, have certain dependencies or have to be equal length or orientation, etc.
% \tias{More detailed description of the properties commented out, feel free to put in}
%Translation:
%\begin{description}
%  \item[Type] Require group that has supertype (e.g. integer => require numeric group, because subgroup might be integer)
%  \item[Length] Require group to have exact length (subgroups have the same length)
%  \item[Vectors / columns / rows] Require group to have at least the amount of vectors, columns, rows required
%  \item[Dependency] Fix dependent variables, for every assignment construct CSP that attempts to find values for the other variables
%  \item[Same length / table / orientation] Require groups to gave the same length table ...
%\end{description}

Constraints derived from the signature can usually but not always be enforced exactly on a group, as we have to consider whether subgroups could satisfy them.
Requirements on the lengths, orientations and tables of groups can be directly enforced since they stay the same for subgroups.
Typing requirements need to be relaxed to consider only non-subtypes, since, for example, numeric groups might contain integer subgroups.
Minimum sizes can be directly enforced, but exact size requirements are relaxed to minimum sizes, since subgroups might contains fewer vectors.
Finally, exact restrictions on the number of rows or columns may have to be relaxed depending on the orientation of the group.
Subgroups of row-oriented (column-oriented) group will always have the same number of columns (rows), however, the number of rows (columns) might decrease.
Therefore, we can only require row-oriented (column-oriented) groups to contain \textit{at least} the required amount of rows (columns).

For example, the \CSignature of ?? requires $v_r$ to be integer.
If a numeric group is assigned to $v_r$ then some subgroups may have type float while other may be of type integer, therefore, this group cannot be discarded.

@@

Note that for some constraint definitions, there are \textit{symmetries} over the arguments that lead to trivially equivalent solutions, for example $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. \samuel{\tias{How are they stopped in the code? should be part of the pseud-code because not part of $Test(X)$?} will make it part of pseudo-code}
